Storm Surges

### 2014-07-08 RoughWork/manuscript.tex
Added a reference

Simulation was run from Feb1-Feb7. The maximum water level observed at Point Atkinson on this day was 5.49 m, which is 0.8 m higher than the predicted tides, highlighting the significance of this event as it resulted in a large anomaly and also reached water levels close to the highest level ever recorded (5.61 m).

@@

The error in modelled residuals at Victoria and Campbell River is also apparent in these figures. Most noticebale is underestimate in modelled residual throughout most of the time period. Additionally, there is a delay of about 2-3 hours in the timing of maximum residual and the relative errors in maximum residual range from 5\% at Point Atkinson to 29\% at Patricia Bay. 
%Question: is it better to present relative errors or just difference?
%I think Hal Ritchie's talk with the storm surges had some stats presented. Look this up...

>>>>

On Feb 4, 2006, a strong storm system with winds over 75 km/hr coinciding with high tide led to siginificant flooding in coastal comminuties of the Strait of Georgia \citep{romanowski2010storm}.    The maximum water level observed at Point Atkinson on this day was 5.49 m, which is 0.8 m higher than the predicted tides, highlighting the significance of this event as it resulted in a large anomaly and also reached water levels close to the highest level ever recorded (5.61 m). The model was run from Feb 1 to 8, 2006 under varying forcing conditions in order to determine the siginicance of each factor contributing to the surge.

@@

The error in modelled residuals at Victoria and Patricia is also apparent in the panels on the right, most noticebale is an underestimate in modelled residual throughout most of the time period. Additionally, there is a delay of about 2-3 hours in the timing of maximum residual at all four locations. The relative errors in maximum residual range from 5\% at Point Atkinson to 29\% at Patricia Bay. 
%Question: is it better to present relative errors or just difference?
%I think Hal Ritchie's talk with the storm surges had some stats presented. Look this up...
